Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-07-14 main.tex
Section 4

\begin{abstract}
    We construct potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulatons. This class of triangulations includes local stars in dimension two and three. 
    The operator norms of our potentials satisfy explicitly computable bounds that only depend on the geometry. 
    We thus obtain computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians. 
    % 
    %     We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
    %     This includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
    %     The main application that we envision are computable estimates over finite element patches. 
    %
    As a result with independent standing, we establish Poincar\'e--Friedrichs inequalities for the $L^{p}$ de~Rham complex over convex bounded domains. 
    This is achieved through bounding operator norms of Poincar\'e and Bogovski\u{\i} potential operators.
    We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances. 
\end{abstract}

@@

The situation is less clear cut when we study the curl or divergence operators in vector calculus.
We use the vector field spaces
\begin{align*}
    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
    ,
    \\
    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
    .
\end{align*}
Their members are vector fields whose distributional curls and divergences are in Lebesgue spaces. 
This only requires that certain sums of distributional partial derivatives are integrable, 
and hence these spaces are not classical Sobolev spaces of vector fields. 
Our objective is to find bounded potentials for the operators 
\begin{align*}
    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
    \qquad 
    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
\end{align*}
The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
We are interested in constants for inequalities such as 
\begin{align*}
    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
    \| \bfv \|_{\bfL^{p}(\Omega)}
    \leq 
    C_{\curl,\Omega,p}
    \| \bff \|_{\bfL^{p}(\Omega)}
    ,
    \qquad 
    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
    \| \bfv \|_{\bfL^{p}(\Omega)}
    \leq 
    C_{\divergence,\Omega,p}
    \| f \|_{L^{p}(\Omega)}
    ,
\end{align*}
and whether these constants can be estimated by the operator norms of linear potential operators 
\begin{align*}
    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
    ,
    \quad 
    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
    .
\end{align*}

@@

When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
which the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. Formally,
\begin{gather*}
    \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T').
\end{gather*}
A crucial observation is the following.

@@

We conclude that taking the average is a projection within Lebegue spaces with unit norm. 

@@

In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. As a preparatory step, 
Given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point. This defines a scalar potential. 
This serves as our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials: 
after fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
\\

% TODO: as for instance recently used in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.

@@

We define the \textit{geometric shape measure} of any $n$-dimensional simplex $T$ as 
\begin{align}\label{math:geometricshapemeasure}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    .
\end{align}
% 
% 
% TODO: Note that \kappa(T)=1 whenever T is a line segment, an isosceles right-angled triangle, or their generalizations to higher dimensions (multiples of a reference simplex). \kappa(T) is slightly bigger than one for equilateral simplices and blows up with distortion.
% 
%

% TODO: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
\begin{align}\label{math:moremeasures}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
%     \qquad 
%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
    \qquad 
    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align}
Here, $\kappa(\calT)$ is the geometric shape measure of the triangulation, and $\rho(\calT)$ is the maximal ratio of volumes between neighboring $n$-simplices. 
Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align}\label{math:reflectionmeasure}
    \xi(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \| \Xi_{S,T} \|.
\end{align}
This indicator quantifies how much reflection across the shared face distorts the geometry.

@@

@@

\begin{remark}
    % Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    In our convention, the reference simplex has unit shape measure.
    This geometric ratio equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

% TODO: INTRODuce a reference simplex 
% TODO: DEFINE THE JACOBIAN

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{align*}
        \| \Jacobian \varphi \|
        \leq 
        \sqrt{n} \cdot \diam(T) % TODO: can this improved?
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \sqrt{2n} 
        % \frac{ n! \vol(T) } { \diam(T)^{n} }
        \kappa(T)^{\frac 1 n}
        \diam(T)^{-1}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
    Thus, $\sigma_1/\sigma_n \leq \sigma_1 / \sqrt[n]{ \det(\Jacobian\varphi) }$ and 
    \[
        \diam(T) 
        \leq 
        \sqrt{2} \sigma_1 
        \leq 
        \sqrt{2} 
        \frac{ \sigma_1 }{ \sqrt[n]{ \det(\Jacobian\varphi) } } 
        \sigma_n
        \leq 
        \sqrt{2n} 
        \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)^{\frac 1 n}
        \sigma_n
        .
    \]
    The desired result is thus evident. % TODO: this is incorrect. Find a better explanation. 
\end{proof}

% TODO: REMOVE THE \cdot 
\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \leq 
        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        % \cdot 
        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        % = 
        \kappa(T_1) \kappa(T_2)
        ,
        \qquad 
        \diam(T_1)
        \leq 
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \diam(F)
        % = 
        \kappa(T_1)
        \diam(F)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
        =  
        \sqrt{2n^{n+1}} 
        \frac{ \kappa(T_1) }{ \kappa(T_2) }
        .
    \end{align*}
\end{lemma}

% TODO: REMOVE THE FACTORIAL?

\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    Then $\vol(T_1) = h_1 \vol(F)/n!$ and $\vol(T_2) = h_2 \vol(F)/n!$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    We estimate 
    % TODO: I am not 100% sure what that means. Is really the heights of F? I imagine this is rather the heights of simplices T_1 and T_2, isn't? Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment! (I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
    % TODO: clarify the first of the following inequalities
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &= n! \frac{\vol(T_2)}{\vol(F)} \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
        .
    \end{align*}
    The first estimate follows. 
    Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
    \begin{align*}
        \diam(F)
        \geq 
        h
        =
        n!
        \frac{ \vol(T_1) }{ \vol(F') }
        \geq 
        \frac{ n! \vol(T_1) }{ \diam(T_1)^{n} }
        \cdot 
        \diam(T_1)
        .
    \end{align*}
    That shows the second estimate. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, we find 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \sqrt{n} 
        \cdot 
        \diam(T_1)
        %
        % \sqrt{2n} \left( \frac{ n! \vol(T_2) } {\diam(T_2)^{n} } \right)^{\frac 1 n}
        \sqrt{2n} \kappa(T_2)^{\frac 1 n}
        \diam(T_2)^{-1}
        \\&
        \leq 
        \sqrt{n} 
        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        \diam(F)
        % \sqrt{2n^{n}} \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
        \sqrt{2n} \kappa(T_2)^{\frac 1 n}
        \diam(F)^{-1}
        \leq 
        n\sqrt{2}
        \kappa(T_1)
        \kappa(T_2)^{\frac 1 n}
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
        .
    \end{align*}
    All the desired results thus follow. % TODO: improve these results, explain in more detail  
    % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
    % \begin{align*}
    %     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
    %     \leq 
    %     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
    %     \cdot 
    %     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
    %     .
    % \end{align*}
\end{proof}

@@

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. 
    Let $U := T_1 \cup T_2$. 
    Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
        \leq 
        2 C_{{\rm EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{{\rm EFNT},p}
        \rho(\calT)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
\end{lemma}
\begin{remark}
    The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
\end{remark}
\begin{proof}
    Let $\hat T_1$ be the reference $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
    Let $\hat U := \hat T_1 \cup \hat T_2$, which is convex. 
    We fix affine diffeomorphisms $\varphi_1 : \hat T_1 \rightarrow T_1$ and $\varphi_2 : \hat T_2 \rightarrow T_2$
    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
    Note that these affine transformations define a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.

>>>>

\begin{abstract}
    We construct potentials for the gradient, the curl and the divergence operators, and more generally the exterior derivative, over domains with shellable triangulations. This class of triangulations includes local stars in dimension two and three. 
    The operator norms of our potentials satisfy explicitly computable bounds that only depend on the geometry. 
    We thus obtain computable upper bounds for Poincar\'e--Friedrichs inequalities and computable lower bounds for the eigenvalues of several vector Laplacians. 
    % 
    %     We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
    %     This includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
    %     The main application that we envision are computable estimates over finite element patches. 
    %
    As a result with independent standing, we establish Poincar\'e--Friedrichs inequalities for the $L^{p}$ de~Rham complex over convex bounded domains. 
    This is achieved through bounding operator norms of Poincar\'e and Bogovski\u{\i} potential operators.
    We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances. 
\end{abstract}

@@

The situation is less clear cut when we study the curl or divergence operators in vector calculus.
We use the vector field spaces
\begin{align*}
    \bfW^{p}(\curl,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \curl \bfu \in \bfL^p(\Omega) \right\}
    ,
    \\
    \bfW^{p}(\divergence,\Omega) &:= \left\{ \bfu \in \bfL^p(\Omega) : \divergence \bfu \in L^p(\Omega) \right\}
    .
\end{align*}
Their members are vector fields whose distributional curls and divergences are in Lebesgue spaces. 
This only requires that certain sums of distributional partial derivatives are integrable, 
and hence these spaces are not classical Sobolev spaces of vector fields. 
Our objective is to find bounded potentials for the operators 
\begin{align*}
    \curl : \bfW^{p}(\curl,\Omega) \rightarrow \bfL^{p}(\Omega),
    \qquad 
    \divergence : \bfW^{p}(\divergence,\Omega) \rightarrow L^{p}(\Omega),
\end{align*}
The fundamental difference to the gradient is that the curl and divergence have infinite-dimensional kernels. 
In the Banach space case, it is not immediately evident that the kernels of these operators are complemented.
The existence of a bounded linear potential operator is a non-trivial fact even in the Hilbert space case.
We are interested in constants for inequalities such as 
\begin{align*}
    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\curl,\Omega) \\ \curl \bfv = \bff } } 
    \| \bfv \|_{L^{p}(\Omega)}
    \leq 
    C_{\curl,\Omega,p}
    \| \bff \|_{L^{p}(\Omega)}
    ,
    \qquad 
    \min\limits_{ \substack{ \bfv \in \bfW^{p}(\divergence,\Omega) \\ \divergence \bfv = f } } 
    \| \bfv \|_{L^{p}(\Omega)}
    \leq 
    C_{\divergence,\Omega,p}
    \| f \|_{L^{p}(\Omega)}
    ,
\end{align*}
and whether these constants can be estimated by the operator norms of linear potential operators 
\begin{align*}
    \Phi_{\curl} : \curl \bfW^{p}(\curl,\Omega) \rightarrow \bfW^{p}(\curl,\Omega)
    ,
    \quad 
    \Phi_{\divergence} : \divergence \bfW^{p}(\divergence,\Omega) \rightarrow \bfW^{p}(\divergence,\Omega)
    .
\end{align*}

@@

When $\calT$ is a triangulation and $T \in \calT$, then $\patch_{\calT}(T)$ denotes the \emph{local patch} or \textit{local star} of $T$, 
which the simplicial subcomplex of $\calT$ that contains all supersimplices of $T$ and their subsimplices. Formally,
\begin{gather*}
    \patch_{\calT}(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T').
\end{gather*}
We write $U_T := | \patch_{\calT}(T) |$ for the underlying set of the local patch. 
A crucial observation is the following.

@@

We conclude that taking the average is a projection within Lebesgue spaces with unit norm. 

@@

In this section we address the stepwise computable estimate of Poincar\'e--Friedrichs constants of triangulated domains. As a preparatory step, 
Given a gradient vector field, we can reconstruct the original scalar function up to a constant by a well-understood procedure: after fixing a starting point, we integrate the gradient vector field along lines emanating from that starting point. This defines a scalar potential. 
This serves as our inspiration for estimating the Poincar\'e constant over triangulated domains, which we achieve by an explicit construction of scalar potentials: 
after fixing a starting triangle, we construct a scalar potential for a given gradient vector field on larger and larger simplicial neighborhoods. 
The basic idea has appeared in the different variants before, for instance recently in \cite{Ern_Voh_p_rob_3D_20, Chaum_Voh_p_rob_3D_H_curl_23, Voh_loc_glob_H1_24}.
\\

@@

@@

We define the \textit{geometric shape measure} of any $n$-dimensional simplex $T$ as 
\begin{align}\label{math:geometricshapemeasure}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    .
\end{align}

\begin{remark}
    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    In our convention, the reference simplex has unit shape measure.
    For example, $\kappa(T)=1$ whenever $T$ is a line segment, an isosceles right-angled triangle, or the generalizations of these reference simplices to higher dimensions. $\kappa(T)$ is slightly bigger than one for equilateral simplices and blows up with distortion.

% Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    The geometric ratio $\kappa(T)$ equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

% DONE: Although this is fairly clear upon reading, we could specify in word that $\kappa(T)$ is (equivalent to) the usual shape regularity parameter, whereas $\rho(\mathcal T)$ is the maximal ratio of volumes between neighboring elements.
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
\begin{align}\label{math:moremeasures}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
%     \qquad 
%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
    \qquad 
    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align}
Here, $\kappa(\calT)$ is the geometric shape measure of the triangulation, and $\rho(\calT)$ is the maximal ratio of volumes between neighboring $n$-simplices. 
Whenever $S,T$ are two $n$-simplices that share a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align}\label{math:reflectionmeasure}
    \xi(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } }
    \| \Jacobian \Xi_{S,T} \|
\end{align}
to be the maximum of the operator norm of the Jacobian of any such diffeomorphism. 
This indicator quantifies how much reflection across the shared face distorts the geometry.

@@

% DONE: INTRODuce a reference simplex 
% DONE: DEFINE THE JACOBIAN 
\todo{MWL: If we need to define the Jacobian formally, where should that be put? Maybe an extra paragraph \textbf{Notation} immediately at the end of the introduction section.}

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\varphi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism from the reference $n$-simplex. Then 
    \begin{align*}
        \| \Jacobian \varphi \|
        \leq 
        \Ceins{n} \cdot \diam(T) % DONE: can this improved?
        ,
        \qquad 
        \| \Jacobian \varphi^{-1} \|
        \leq 
        \Czwei{n} \cdot 
        \kappa(T) 
        \diam(T)^{-1}
        .
    \end{align*}
    Here, $\Ceins{n} \leq \sqrt{n}$ and $\Czwei{n} \leq \sqrt{ 2n/(n-1)^{n-1} }$. 
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of the Jacobian $\Jacobian\varphi$ in descending order.
    The Jacobian determinant is the product of these singular values. 
%     By a result of Hong and Pan,
%     \begin{align*}
%         \frac{ \sigma_{n} }{ \sigma_{1} }
%         \geq 
%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ \| \Jacobian\varphi \| }
%         \sigma_{1}^{-1}
%         \geq 
%         \left(\frac{n-1}{n}\right)^{\frac{n-1}{2}}
%         \frac{ \sqrt{n} \det(\Jacobian\varphi) }{ n \sigma_{1} }
%         \sigma_{1}^{-1}
%         .
%     \end{align*}
    By a result of Yu and Gu \cite{yisheng1997note},
    \begin{align*}
        \frac{ \sigma_{n} }{ \sigma_{1} }
        &\geq 
        \det(\Jacobian\varphi)
        \left( \frac{n-1}{\|\Jacobian\varphi\|_{F}^{2}} \right)^{\frac{n-1}{2}}
        \sigma_{1}^{-1}
%         \geq 
%         (n-1)^{\frac{n-1}{2}}
%         \det(\Jacobian\varphi)
%         \left( \frac{1}{ \diam(T)^{n-1} } \right)^{}
%         \frac{1}{\sqrt{n} \diam(T)}
%         \\&
%         \geq 
%         \frac{1}{\sqrt{n}}
%         (n-1)^{\frac{n-1}{2}}
%         \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
        \geq 
        \sqrt{\frac{ (n-1)^{n-1} }{n} }
        \frac{ \det(\Jacobian\varphi) }{ \diam(T)^{n} }
        .
    \end{align*}
    Since $\diam(T) \leq \sqrt{2} \sigma_{1}$, the desired result follows. 
%     Thus, $\sigma_1/\sigma_n \leq \sigma_1^{n} / { \det(\Jacobian\varphi) }$ and 
%     \[
%         \diam(T) 
%         \leq 
%         \sqrt{2} \sigma_1 
%         \leq 
%         \sqrt{2} 
%         \frac{ \sigma_1^{n} }{ { \det(\Jacobian\varphi) } } 
%         \sigma_n
%         \leq 
%         \sqrt{2n^{n}} 
%         \left( \frac{ \diam(T)^{n} }{ n! \vol(T) } \right)
%         \sigma_n
%         .
%     \]
%     The desired result is thus evident. 
\end{proof}

% TODO: REMOVE THE \cdot 
\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \diam(T_1)
        \leq 
        % \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        % \diam(F)
        % = 
        \kappa(T_1)
        \diam(F)
        ,
        \qquad 
        \frac{ \vol(T_1) }{ \vol(T_2) }
        \leq 
        % \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        % \cdot 
        % \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        % = 
        \kappa(T_1) \kappa(T_2)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \Cdrei{n}
        \frac{ \kappa(T_1) }{ \kappa(T_2) }
        .
    \end{align*}
    Here, $\Cdrei{n} \leq \Ceins{n} \Czwei{n}$. 
\end{lemma}

% Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
% \begin{align*}
%     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
%     \leq 
%     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
%     \cdot 
%     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
%     .
% \end{align*}
% DONE: REMOVE THE FACTORIAL?
% DONE: I am not 100% sure what that means. Is really the heights of F? I imagine this is rather the heights of simplices T_1 and T_2, isn't? Maybe the wording you use is standard and I simply don't know about it, if so, please ignore the comment! (I mean, I am probably being too pedantic here, what you mean is completely clear from the next sentence).
% DONE: clarify the first of the following inequalities

%     \begin{align*}
%         \diam(F) \geq h_S = n \frac{ \vol(T_1) }{ \vol(S) } \geq n \frac{ \vol(T_1) }{ \diam(T_1)^{n} } \diam(T_1).
%     \end{align*}
%     Thus we establish the first estimate:

%     Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
%     \begin{align*}
%         \diam(F)
%         \geq 
%         h
%         =
%         n
%         \frac{ \vol(T_1) }{ \vol(F') }
%         \geq 
%         \frac{ n \vol(T_1) }{ \diam(T_1)^{n} }
%         \cdot 
%         \diam(T_1)
%         .
%     \end{align*}
%     That shows the second estimate.

\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    By the volume formula for simplices, $\vol(T_1) = h_1 \vol(F)/n$ and $\vol(T_2) = h_2 \vol(F)/n$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    The diameter of $F$ is at least as large as the height $h_S$ of some other facet $S$ of $T$. Recursive application of the volume formula shows 
    \begin{align*}
        \vol(T) = \frac{1}{n!} h_S h_2 \cdots h_n,
    \end{align*}
    where $h_S \leq \diam(F)$ and $h_2, \cdots, h_n \leq \diam(T)$. Now, 
    \begin{align*}
        \diam(T) \frac{ n! \vol(T) }{ \diam(T)^{n} } \leq h_S \leq \diam(F).
    \end{align*}
    The first estimate follows. 
    On the other hand, 
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &= n \frac{\vol(T_2)}{\vol(F)} \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
        .
    \end{align*}
    The second estimate follows. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, Lemma~\eqref{lemma:affinetransform} and the first estimate imply 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \diam(T_1)
        \diam(T_2)^{-1}
        \\&
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \kappa(T_1) 
        \diam(F)
        \diam(T_2)^{-1}
        \leq 
        \Ceins{n}
        \Czwei{n}
        \kappa(T_2)
        \kappa(T_1) 
        .
    \end{align*}
    All the desired results thus follow.
\end{proof}

@@

\begin{lemma}\label{lemma:poincarefriedrichsoverfacepatch}
    Suppose that $T, T'$ are two $n$-simplices whose intersection is a common face $F := T_1 \cap T_2$. 
    Write $U := T_1 \cup T_2$. 
    Then 
    \begin{align*}
        \min\limits_{ c \in \bbR }
        \| u - c \|_{L^{p}(U)}
        &
        \leq 
        2 C_{{\rm EFNT},p}
        \max\left( 
            \frac{ \vol(T_1) }{ \vol(T_2) }
            ,
            \frac{ \vol(T_2) }{ \vol(T_1) }
        \right)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        \\&
        \leq 
        2 C_{{\rm EFNT},p}
        \rho(\calT)^{\frac 1 p}
        \max\left( \diam(T_1), \diam(T_2) \right)
        \| \nabla u \|_{L^{p}(U)}
        .
    \end{align*}
    for any $u \in W^{1,p}(\Omega)$ with $p \in [1,\infty]$.
\end{lemma}
% \begin{remark}
%     The result is sharp when $T_1$ and $T_2$ have equal volume and diameter, and that $U$ is not necessarily convex. 
% \end{remark}
\begin{proof}
    Let $\hat T_1$ be the reference $n$-simplex whose vertices $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v_n = e_n$ are the origin and the $n$ canonical unit vectors. 
    We let $\hat T_2$ be the $n$-simplex whose vertices are $v_0=0, v_1=e_1, \dots, v_{n-1} = e_{n-1}, v'_n = -e_n$. 
    Let $\hat U := \hat T_1 \cup \hat T_2$, which is convex. 
    We fix affine diffeomorphisms $\varphi_1 : \hat T_1 \rightarrow T_1$ and $\varphi_2 : \hat T_2 \rightarrow T_2$
    which map the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F$.
    Note that these affine transformations define a bi-Lipschitz mapping $\varphi : \hat U \rightarrow U$.
